---
title: "Hello R"
author: "Christian Tuarez"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 5
    highlight: kate
    theme: yeti
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen dataframe contains 1846 rows and 3 columns.
The datasaurus_dozen dataframe contains 3 variables:

- __dataset__: indicates which dataset the data are from
- __x__: x-values
- __y__: y-valuesda

### Exercise 2

Plotting the data in the dino dataset:

```{r plot-dino, fig.height=4, fig.width=8}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotting the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between `x` and `y` in this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

For the dino dataset, the r value is -0.0645. For the star dataset, the r value is -0.0630.

### Exercise 4

Plotting the data in the circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

For the dino dataset, the r value is -0.0645. For the circle dataset, the r value is -0.0683.

### Exercise 5

Plotting all 13 datasets in the datasaurus_dozen dataframe:

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

Plotting r values for all 13 datasets in the datasaurus_dozen dataframe:

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print()
```

